Predicting structure--function relationships using natural genetic variation

### 2018-10-19 manuscript/03-AFBs.Rmd
compiled to word and sent to Jennifer for feedback

if (knitr::is_html_output()) {
  formatRound(datatable(div_stats,
                  colnames = c("transcript",
                               "symbol",
                               "&pi;<sub>N</sub>",
                               "&pi;<sub>S</sub>",
                               "&pi;<sub>N</sub>/&pi;<sub>S</sub>",
                               "&pi; coding",
                               "&pi; transcript"),
                  rownames = FALSE, escape = FALSE,
                  options = list(paging=FALSE, searching=FALSE)),
                columns = 2:7, digits = 6)
  } else 
{
  dt <- div_stats
  names(dt) <- c("transcript",
                                 "symbol",
                                 "&pi;~N~",
                                 "&pi;~S~",
                                 "&pi;~N~/&pi;~S~",
                                 "&pi; coding",
                                 "&pi; transcript")
  dt %<>% mutate_if(is.numeric, round, 6)
  names(dt) <- paste0("**", names(dt), "**")
  kable(dt, caption = "(\\#tab:TIR1AFBdivstats)") 
}
```

@@

```{r Mask_AFB_alignment, eval=FALSE}
aliscore(as.AAbin(alignment[[2]]), path = "/Volumes/SSD/Applications/ALISCORE_v2.0/Aliscore_v.2.0/",  o = "AT2G39940")
id <- scan(file = "/Volumes/SSD/Applications/ALISCORE_v2.0/Aliscore_v.2.0/input.fas_List_random.txt", sep = " ", quiet = TRUE)
AAAlign_no_gaps <- as.matrix(alignment[[2]])[, id]
write.nexus.data(AAAlign_no_gaps, file = "trees/AFBs.nex", format = "protein")
```
```{bash IAA_phylogeny_construction, eval=FALSE}
cd ~/Desktop/natural-variation-webtool/manuscript/trees

@@

```{r AFBtree, fig.height=2, fig.width=3, fig.cap="(ref:AFBtree)"}
p <- ggtree(tree, layout = "rectangular", color = "grey") %<+% AFB_data + theme_tree() + scale_x_continuous(expand = c(0, 1.2)) + 
  geom_tippoint(mapping = aes(size = 4*Pi_NS_Ratio, fill = Pi_NS_Ratio), shape = 21, color = "white", show.legend = TRUE) + 
  scale_fill_viridis(values = rescale(c(min(AFB_data$Pi_NS_Ratio),
                                        max(AFB_data$Pi_NS_Ratio)), 
                                      to = c(0,1)), guide = "colourbar") + scale_size(guide = "none") + 
  theme(legend.position = c(.1,.7)) + 
  geom_nodelab(mapping = aes(label = round(prob,digits = 2)), nudge_x = -.3, nudge_y = .5, size = 3) + 
  geom_tiplab(hjust = -0.25) + 
  scale_color_viridis(discrete = TRUE)
p
#ggsave("AFBs_tree.pdf", height = 3, width = 4)
```

@@

aln_df <- left_join(aln_df, dplyr::select(gene_info, "tair_locus",
                                       "tair_symbol", "transcript_ID"),
                        by = c("transcript_ID" = "transcript_ID"))
aln_df$tair_symbol %<>% factor(levels = AFB_order, 
                                       ordered = TRUE)
aln_df$tair_symbol %<>% fct_rev()

@@

p <-ggplot(aln_df, aes(x = aln_pos, y = tair_symbol)) +
  geom_raster(data = aln_df, 
             # mapping = aes(fill = effects)) +
              mapping = aes(fill = strength,
                            alpha = gap)) +
  scale_alpha_manual(values = c("TRUE" = 0, "FALSE" = 1), 
                     labels = c("aligned", "gap"), 
                     guide = guide_legend(override.aes = 
                                            list(fill = c("grey85", "white")),
                       title = "alignment",
                       direction = "vertical")) + 
   scale_fill_viridis(breaks = range(effect_order$strength),
                      limits = range(effect_order$strength),
                      na.value = "grey85",
                      direction = -1,
                      labels = c("neutral", "deleterious"),
                      option = "A", 
                      guide = guide_colorbar(ticks = FALSE, 
                                             title.vjust = .8, 
                                             title.position = "top", 
                                             title.hjust = 0.5)) +
  scale_y_discrete(expand = c(0,0)) +
  scale_x_continuous(expand = c(0,0)) +  # expand increases distance from axis
  labs(x = "codon position in alignment", y = "", fill = "variant effect") +
  theme_logo(base_family = "Helvetica") +
  theme(panel.grid = element_blank(), 
        panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        strip.text.x = element_blank(),
        #panel.background = element_rect(fill = "grey85", color = "white"),
        legend.position = c("bottom"),
        legend.key = element_rect(linetype = "solid"),
        legend.spacing = unit(4, "char"), 
        legend.box.spacing = unit(0.1,"line")) 
p

@@

```{r AFB variants for PyMOL}
coding_vcf <- ldply(.data = VCF, .fun = subset, 
             !is.na(Transcript_ID) & gt_GT != "0|0")
aln_df <- addSNPsToAlnDF(aln_df, coding_vcf, seq_name = Transcript_ID, 
               seq_pos = Codon_Number)
collapsed_aln_df %<>% left_join(y = subset(aln_df, seq_name == gene_info[gene_info$tair_symbol == "TIR1", "transcript_ID"]))

@@

```{r AFB1 diversity plot}
coding_variants <- getCodingDiv(VCF[[gene_info[gene_info$tair_symbol == "AFB1", "transcript_ID"]]])
p <- plotCodingDiv(uniqueCodingVars = coding_variants)
annotation <- readAnnotationFile(filename = system.file("shiny-app", "gene_family_data",
                      "AFB_annotations.csv", package = "r1001genomes"), gene_info = gene_info)
annotation <- addAlnPosToAnno(anno_df = annotation, aln_df)

@@

```{r FBoxAlignment, fig.cap = "(ref:FBoxAlignment)"}
aln_df <- makeAlnDF(alignment[[2]])
aln_df <- left_join(aln_df, dplyr::select(gene_info, "tair_locus",
                                       "tair_symbol", "transcript_ID"),
                        by = c("transcript_ID" = "transcript_ID"))
aln_df$tair_symbol <- fct_rev(fct_relevel(aln_df$tair_symbol, "TIR1"))
aln_df <- chunkAlnDF(aln_df = aln_df, chunk_width = 55)
VCF <- ldply(.data = VCF, .fun = subset, gt_GT != "0|0")
VCF <- getCodingDiv(VCF)
aln_df <- addSNPsToAlnDF(aln_df, VCF)
F_box <- subset(aln_df, aln_pos <= 96)
F_box <- chunkAlnDF(aln_df = F_box, chunk_width = 80)
p <-ggplot(F_box, aes(x = aln_pos, y = tair_symbol,
                             group = seq_pos, text = variants))
p <- p +
  geom_tile(data = na.omit(F_box), mapping = aes(fill = effects),
            width = 1, height = 1, alpha = 0.8) +
  geom_text(aes(label=letter), alpha= 1, family = "Courier") +
  scale_fill_brewer(type = "qual", palette = 1, direction = -1) +
  scale_x_continuous(breaks=seq(1,max(F_box$aln_pos), by = 10)) +
  scale_y_discrete() +
  # expand increases distance from axis
  labs(x = "", y = "", fill = "variant") +
  theme_logo(base_family = "Helvetica") +
  theme(panel.grid = element_blank(), panel.grid.minor = element_blank()) +
  facet_wrap(facets = ~chunk, ncol = 1, scales = "free") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank(),
        legend.box = "vertical")
p
```

>>>>

if (knitr::is_html_output()) {
  formatRound(datatable(div_stats,
                  colnames = c("transcript",
                               "symbol",
                               "&pi;<sub>N</sub>",
                               "&pi;<sub>S</sub>",
                               "&pi;<sub>N</sub>/&pi;<sub>S</sub>",
                               "&pi; coding",
                               "&pi; transcript"),
                  rownames = FALSE, escape = FALSE,
                  options = list(paging=FALSE, searching=FALSE)),
                columns = 2:7, digits = 6)
  } else 
{
  dt <- div_stats
  names(dt) <- c("transcript",
                                 "symbol",
                                 "&pi;~N~",
                                 "&pi;~S~",
                                 "&pi;~N~/&pi;~S~",
                                 "&pi; coding",
                                 "&pi; transcript")
  dt %<>% mutate_if(is.numeric, round, 6)
  names(dt) <- paste0("**", names(dt), "**")
  kable(dt) 
}
```

@@

```{r Mask_AFB_alignment, eval=FALSE}
aliscore(as.AAbin(alignment[[2]]), path = "/Volumes/SSD/Applications/ALISCORE_v2.0/Aliscore_v.2.0/",  o = "AT2G39940")
id <- scan(file = "/Volumes/SSD/Applications/ALISCORE_v2.0/Aliscore_v.2.0/input.fas_List_random.txt", sep = " ", quiet = TRUE)
AAAlign_no_gaps <- as.matrix(alignment[[2]])[, id]
write.nexus.data(AAAlign_no_gaps, file = "trees/AFBs.nex", format = "protein")
```
```{bash AFB_phylogeny_construction, eval=FALSE}
cd ~/Desktop/natural-variation-webtool/manuscript/trees

@@

```{r AFBtree, fig.height=2, fig.width=3, fig.cap="(ref:AFBtree)"}
p <- ggtree(tree, layout = "rectangular", color = "grey") %<+% AFB_data + theme_tree() + scale_x_continuous(expand = c(0, 1.2)) + 
  geom_tippoint(mapping = aes(size = 4*Pi_NS_Ratio, fill = Pi_NS_Ratio), shape = 21, color = "white", show.legend = TRUE) + 
  scale_fill_viridis(values = rescale(c(min(AFB_data$Pi_NS_Ratio),
                                        max(AFB_data$Pi_NS_Ratio)), 
                                      to = c(0,1)), guide = "colourbar") + scale_size(guide = "none") +
  labs(fill = expression(pi [N] / pi [S])) + 
  theme(legend.position = c(.1,.7)) + 
  #geom_nodelab(mapping = aes(label = node)) +
  geom_nodelab(mapping = aes(label = round(as.numeric(prob),digits = 2)), nudge_x = -.2, nudge_y = .2, size = 3) + 
  geom_tiplab(hjust = -0.25) + 
  scale_color_viridis(discrete = TRUE)  
p <- p %>% ggtree::rotate(12) %>% ggtree::rotate(9)
p
#ggsave("AFBs_tree.pdf", height = 3, width = 4)
```

@@

aln_df <- left_join(aln_df, dplyr::select(gene_info, "tair_locus",
                                       "tair_symbol", "transcript_ID"),
                        by = c("transcript_ID" = "transcript_ID"))
aln_df$tair_symbol %<>% factor(levels = AFB_order, 
                                       ordered = TRUE)
aln_df$tair_symbol %<>% fct_rev()
VCF <- ldply(.data = VCF, .fun = subset, gt_GT != "0|0")
VCF <- getCodingDiv(VCF)

@@

p <-ggplot(subset(aln_df, tair_symbol != "COI1"), aes(x = aln_pos, y = tair_symbol)) +
  geom_raster(mapping = aes(fill = strength,
                            alpha = gap)) +
  scale_alpha_manual(values = c("TRUE" = 0, "FALSE" = 1), 
                     labels = c("aligned", "gap"), 
                     guide = guide_legend(override.aes = 
                                            list(fill = c("grey85", "white")),
                       title = "alignment",
                       direction = "vertical")) + 
   scale_fill_viridis(breaks = range(SNPeff_order$strength),
                      limits = range(SNPeff_order$strength),
                      na.value = "grey85",
                      direction = -1,
                      labels = c("neutral", "deleterious"),
                      option = "A", 
                      guide = guide_colorbar(ticks = FALSE, 
                                             title.vjust = .8, 
                                             title.position = "top", 
                                             title.hjust = 0.5)) +
  scale_y_discrete(expand = c(0,0)) +
  scale_x_continuous(expand = c(0,0)) +  # expand increases distance from axis
  labs(x = "codon position in alignment", y = "", fill = "variant effect") +
  theme_logo(base_family = "Helvetica") +
  theme(panel.grid = element_blank(), 
        panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        strip.text.x = element_blank(),
        #panel.background = element_rect(fill = "grey85", color = "white"),
        legend.position = c("bottom"),
        legend.key = element_rect(linetype = "solid"),
        legend.spacing = unit(4, "char"), 
        legend.box.spacing = unit(0.1,"line")) 
p

@@

```{r AFB variants for PyMOL, eval=FALSE}
coding_vcf <- ldply(.data = VCF, .fun = subset, 
             !is.na(transcript_ID) & gt_GT != "0|0")
aln_df <- addSNPsToAlnDF(aln_df, coding_vcf, seq_name = Transcript_ID, 
               seq_pos = Codon_Number)
collapsed_aln_df %<>% left_join(y = subset(aln_df, seq_name == gene_info[gene_info$tair_symbol == "TIR1", "transcript_ID"]))

@@

```{r AFB1 diversity plot}
coding_variants <- VCF[VCF$Transcript_ID == gene_info[gene_info$tair_symbol == "AFB1", "transcript_ID"], ]
p <- plotCodingDiv(uniqueCodingVars = coding_variants)
annotation <- readAnnotationFile(filename = system.file("shiny-app", "gene_family_data",
                      "AFB_annotations.csv", package = "r1001genomes"), gene_info = gene_info)
annotation <- addAlnPosToAnno(anno_df = annotation, aln_df)

@@

```{r FBoxAlignment, fig.cap = "(ref:FBoxAlignment)"}
aln_df <- makeAlnDF(alignment[[2]])
aln_df <- left_join(aln_df, dplyr::select(gene_info, "tair_locus",
                                       "tair_symbol", "transcript_ID"),
                        by = c("transcript_ID" = "transcript_ID"))
aln_df$tair_symbol <- fct_rev(fct_relevel(aln_df$tair_symbol, "TIR1"))
aln_df <- chunkAlnDF(aln_df = aln_df, chunk_width = 55)
aln_df <- addSNPsToAlnDF(aln_df, VCF, effect_order = SNPeff_order)
F_box <- subset(aln_df, aln_pos <= 96)
F_box <- chunkAlnDF(aln_df = F_box, chunk_width = 80)
p <-ggplot(F_box, aes(x = aln_pos, y = tair_symbol,
                             group = seq_pos, text = variants))
p <- p +
  geom_tile(data = na.omit(F_box), mapping = aes(fill = effects),
            width = 1, height = 1, alpha = 0.5) +
  geom_text(aes(label=letter), alpha= 1, family = "Courier") +
  scale_x_continuous(breaks=seq(1,max(F_box$aln_pos), by = 10)) +
  scale_y_discrete() +
  # expand increases distance from axis
  labs(x = "", y = "") +
  theme_logo(base_family = "Helvetica") +
  theme(panel.grid = element_blank(), panel.grid.minor = element_blank()) +
  facet_wrap(facets = ~chunk, ncol = 1, scales = "free") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank(),
        legend.box = "vertical") + 
  scale_fill_viridis(option = "A", discrete = TRUE)
p
```

### 2018-10-19 manuscript/05-TPLs.Rmd
compiled to word and sent to Jennifer for feedback

```{r TPL SNP stats, fig.height=11}
gene_info <- geneInfoFromFile(
  fname = system.file("shiny-app", "gene_family_data",
                      "TPL_gene_ids.csv", package = "r1001genomes"))
#annotation <- readAnnotationFile(filename = system.file("shiny-app", "gene_family_data",
#                      "IAA_annotations.csv", package = "r1001genomes"), gene_info = gene_info)

@@

#get
VCF <- ldply(.data = VCF, .fun = subset, gt_GT != "0|0")
VCF <- getCodingDiv(VCF)
effect_order <- read.csv("~/Desktop/SNPeff_order.csv")

@@

```{r Mask_ARF_alignment, eval=FALSE}
aliscore(as.AAbin(alignment[[2]]), path = "/Volumes/SSD/Applications/ALISCORE_v2.0/Aliscore_v.2.0/")
id <- scan(file = "/Volumes/SSD/Applications/ALISCORE_v2.0/Aliscore_v.2.0/input.fas_List_random.txt", sep = " ", quiet = TRUE)
AAAlign_no_gaps <- as.matrix(alignment[[2]])[, id]
write.nexus.data(AAAlign_no_gaps, file = "TPLs.nex", format = "protein")
```
```{bash ARF_phylogeny_construction, eval=FALSE}
/Applications/MrBayes/mb

@@

TPL_data <- read.csv(system.file("shiny-app", "gene_family_data",
                      "TPL_gene_ids.csv", package = "r1001genomes"))
TPL_data %<>% left_join(y = div_stats, by = c("name" = "tair_symbol"))
#tip_labels need to be in the first column
TPL_data %<>% dplyr::select(name, everything())
TPL_data$tair_locus %<>% as.character()

@@

```{r Visualize TPL tree, fig.height=5, fig.width=5}
p <- ggtree(tree, layout = "rectangular", color = "grey") %<+% 
  TPL_data + theme_tree() + scale_x_continuous(expand = c(0, 1.2)) +
  geom_hilight(node = 28, extend = 1) + 
  geom_hilight(node = 25, extend = 1) +
  geom_tippoint(mapping = 
                  aes(size = 4*Pi_NS_Ratio, fill = Pi_NS_Ratio),
                shape = 21, color = "white", show.legend = TRUE,
                position = position_nudge(x = 0.01)) + 
  geom_rootpoint(color = "grey") + 
  scale_fill_viridis(values = rescale(
    c(min(TPL_data$Pi_NS_Ratio),
      max(TPL_data$Pi_NS_Ratio)), 
                                    to = c(0,1)), guide = "colourbar") +
  scale_size(guide = "none") + 
  theme(legend.position = c(.1,.7)) + 
  geom_nodelab(mapping = aes(label = node), nudge_x = -.2, size = 3)
  #geom_nodelab(mapping = aes(label = round(prob,digits = 2)), nudge_x = -.25, size = 3) +
  #geom_tiplab(mapping = aes(color = class), hjust = -0.3) + 
p
```

```{r full-ARFs-alignment}
ARF_order <- fct_inorder(na.exclude(p$data$label[base::order(p$data$y, decreasing = TRUE)]), ordered = TRUE)

aln_df <- left_join(aln_df, dplyr::select(gene_info, "tair_locus",
                                       "tair_symbol", "transcript_ID"),
                        by = c("transcript_ID" = "transcript_ID"))
aln_df$tair_symbol %<>% factor(levels = ARF_order, 
                                       ordered = TRUE)
aln_df$tair_symbol %<>% fct_rev()

aln_df <- addSNPsToAlnDF(aln_df, VCF, effect_order = effect_order)
aln_df$gap <- aln_df$seq_pos == "-"

p <-ggplot(aln_df, aes(x = aln_pos, y = tair_symbol)) +
  geom_raster(data = aln_df, 
             # mapping = aes(fill = effects)) +
              mapping = aes(fill = strength,
                            alpha = gap)) +
  scale_alpha_manual(values = c("TRUE" = 0, "FALSE" = 1), 
                     labels = c("aligned", "gap"), 
                     guide = guide_legend(override.aes = 
                                            list(fill = c("grey85", "white")),
                       title = "alignment",
                       direction = "vertical")) + 
   scale_fill_viridis(breaks = range(effect_order$strength),
                      limits = range(effect_order$strength),
                      na.value = "grey85",
                      direction = -1,
                      labels = c("neutral", "deleterious"),
                      option = "A", 
                      guide = guide_colorbar(ticks = FALSE, 
                                             title.vjust = .8, 
                                             title.position = "top", 
                                             title.hjust = 0.5)) +
  scale_y_discrete(expand = c(0,0)) +
  scale_x_continuous(expand = c(0,0)) +  # expand increases distance from axis
  labs(x = "codon position in alignment", y = "", fill = "variant effect") +
  theme_logo(base_family = "Helvetica") +
  theme(panel.grid = element_blank(), 
        panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        strip.text.x = element_blank(),
        #panel.background = element_rect(fill = "grey85", color = "white"),
        legend.position = c("bottom"),
        legend.key = element_rect(linetype = "solid"),
        legend.spacing = unit(4, "char"), 
        legend.box.spacing = unit(0.1,"line")) 
p

>>>>

```{r TPL SNP stats, fig.height=11}
gene_info <- geneInfoFromFile(
  fname = system.file("shiny-app", "gene_family_data",
                      "TPL_gene_ids.csv", package = "r1001genomes"))
#annotation <- readAnnotationFile(filename = system.file("shiny-app", "gene_family_data",
#                      "TPL_annotations.csv", package = "r1001genomes"), gene_info = gene_info)

@@

#get
VCF <- ldply(.data = VCF, .fun = subset, gt_GT != "0|0")
VCF <- getCodingDiv(VCF)

@@

```{r Mask_TPL_alignment, eval=FALSE}
aliscore(as.AAbin(alignment[[2]]), path = "/Volumes/SSD/Applications/ALISCORE_v2.0/Aliscore_v.2.0/")
id <- scan(file = "/Volumes/SSD/Applications/ALISCORE_v2.0/Aliscore_v.2.0/input.fas_List_random.txt", sep = " ", quiet = TRUE)
AAAlign_no_gaps <- as.matrix(alignment[[2]])[, id]
write.nexus.data(AAAlign_no_gaps, file = "TPLs.nex", format = "protein")
```
```{bash TPL_phylogeny_construction, eval=FALSE}
/Applications/MrBayes/mb

@@

TPL_data <- read.csv(system.file("shiny-app", "gene_family_data",
                      "TPL_gene_ids.csv", package = "r1001genomes"))
TPL_data$name <- as.character(TPL_data$name)
TPL_data %<>% left_join(y = div_stats, by = c("name" = "tair_symbol"))
#tip_labels need to be in the first column
TPL_data %<>% dplyr::select(name, everything())
TPL_data$tair_locus %<>% as.character()

@@

```{r Visualize TPL tree, fig.height=2, fig.width=3}
p <- ggtree(tree, layout = "rectangular", color = "grey") %<+% TPL_data + theme_tree() + scale_x_continuous(expand = c(0, 1.2)) + 
  geom_tippoint(mapping = aes(size = 4*Pi_NS_Ratio, fill = Pi_NS_Ratio), shape = 21, color = "white", show.legend = TRUE) + 
  scale_fill_viridis(values = rescale(c(min(TPL_data$Pi_NS_Ratio),
                                        max(TPL_data$Pi_NS_Ratio)), 
                                      to = c(0,1)), guide = "colourbar") + scale_size(guide = "none") +
  labs(fill = expression(pi [N] / pi [S])) + 
  theme(legend.position = c(.1,.7)) + 
  #geom_nodelab(mapping = aes(label = node)) +
  geom_nodelab(mapping = aes(label = round(as.numeric(prob),digits = 2)), nudge_x = -.2, nudge_y = .2, size = 3) + 
  geom_tiplab(hjust = -0.25) 
p
```

(ref:full-TPLs-alignment) **Alignment of A. thaliana TPL/TPR genes showing variants.** This alignment should probably be paired down to a key region rather than the eniter AA sequence.

```{r full-TPLs-alignment, fig.cap= "(ref:full-TPLs-alignment)"}
TPL_order <- fct_inorder(na.exclude(p$data$label[base::order(p$data$y, decreasing = TRUE)]), ordered = TRUE)

aln_df <- left_join(aln_df, dplyr::select(gene_info, "tair_locus",
                                       "tair_symbol", "transcript_ID"),
                        by = c("transcript_ID" = "transcript_ID"))
aln_df$tair_symbol %<>% factor(levels = TPL_order, 
                                       ordered = TRUE)
aln_df$tair_symbol %<>% fct_rev()

aln_df <- addSNPsToAlnDF(aln_df, VCF, effect_order = SNPeff_order)
aln_df$gap <- aln_df$seq_pos == "-"

p <-ggplot(aln_df, aes(x = aln_pos, y = tair_symbol)) +
  geom_raster(data = aln_df, 
             # mapping = aes(fill = effects)) +
              mapping = aes(fill = strength,
                            alpha = gap)) +
  scale_alpha_manual(values = c("TRUE" = 0, "FALSE" = 1), 
                     labels = c("aligned", "gap"), 
                     guide = guide_legend(override.aes = 
                                            list(fill = c("grey85", "white")),
                       title = "alignment",
                       direction = "vertical")) + 
   scale_fill_viridis(breaks = range(SNPeff_order$strength),
                      limits = range(SNPeff_order$strength),
                      na.value = "grey85",
                      direction = -1,
                      labels = c("neutral", "deleterious"),
                      option = "A", 
                      guide = guide_colorbar(ticks = FALSE, 
                                             title.vjust = .8, 
                                             title.position = "top", 
                                             title.hjust = 0.5)) +
  scale_y_discrete(expand = c(0,0)) +
  scale_x_continuous(expand = c(0,0)) +  # expand increases distance from axis
  labs(x = "codon position in alignment", y = "", fill = "variant effect") +
  theme_logo(base_family = "Helvetica") +
  theme(panel.grid = element_blank(), 
        panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        strip.text.x = element_blank(),
        #panel.background = element_rect(fill = "grey85", color = "white"),
        legend.position = c("bottom"),
        legend.key = element_rect(linetype = "solid"),
        legend.spacing = unit(4, "char"), 
        legend.box.spacing = unit(0.1,"line")) 
p
